Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-20 Draft_arXiv/article.tex
Typo fixed
Final description of Whizard

The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
radiated off the quark lines. Because of the different colour structure, this contribution features a 
different kinematic behaviour than VBS.
Nonetheless it shares the same final state, and therefore constitutes an irreducible background to EW process.

@@

      \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
          event generator with the LO matrix element generator {\sc O'Mega}. \ZM{ if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
    It provides FKS subtraction terms for any NLO process, while virtual matrix
    elements are provided externally by {\sc
    OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
    (\emph{cf.}\ above) can be used as well). {\sc Whizard} allows to simulate a
    huge number of BSM models as well, in particular in
    the VBS channels in terms of both higher-dimensional operators as well as explicit
    resonances.

>>>>

The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
radiated off the quark lines. Because of the different colour structure, this contribution features a 
different kinematic behaviour than VBS.
Nonetheless it shares the same final state, and therefore constitutes an irreducible background to the EW process.

@@

      \item WHIZARD~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
      For QCD amplitudes it uses the colour flow formalism~\cite{Kilian:2012pz}.
      For NLO QCD calculations~\cite{Nejad:2016bci}, where WHIZARD is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
      Furthermore, WHIZARD can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
      WHIZARD allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
